% Copyright 2022 Daniel Wierdsma
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%    http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

%% Extended Article for font-size
\documentclass[9pt]{extarticle}

%% Black and White vs Design
%\newcommand*{\PRINT}{}

%% Font
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\usepackage{fontawesome}
\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{20pt}{24pt}}
\makeatother

%% Packages
\usepackage{color}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{scrextend}
\usepackage{tabto}
\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

%% Page Indentation and Line Spacing
\setlength{\parskip}{10pt}
\setlength{\parindent}{0pt}
\linespread{1.1}
\pagenumbering{gobble}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.75in}

%% Custom Colours
\definecolor{linkblue}{RGB}{6,69,173}
\definecolor{darkgrey}{RGB}{75,75,75}
\definecolor{mediumgrey}{RGB}{102,102,102}

\ifdefined\PRINT
    \definecolor{em-light}{RGB}{0,0,0}
    \definecolor{lightgrey}{RGB}{225,225,225}
\else
    \definecolor{em-light}{RGB}{25,130,232}
    \definecolor{lightgrey}{RGB}{25,130,232}
\fi

%% Word Wrap
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}

%%Begin%% Header
{
    \begin{tabularx}{\textwidth}{Xr}
    {\HUGE\leavevmode\color{em-light} Daniel Wierdsma} &
        \null\hfill\small\begin{tabular}{llX}
            \faMapMarker\space\space\space\color{darkgrey} Toronto, Ontario, Canada & \faEnvelope\space\space\color{darkgrey} \href{mailto:dan.wierdsma@gmail.com}{dan.wierdsma@gmail.com} \\[3px]
            \faGithub\space\space\color{darkgrey} \href{https://github.com/d-wierdsma}{github.com/d-wierdsma} & {\large\faMobilePhone}\space\space\space\color{darkgrey} +1 (519) 635 4151 \\[10px]
        \end{tabular}
    \end{tabularx}

    {\color{lightgrey}{\centerline{\rule{17cm}{0.4pt}}}}
}
%%End%% Header
%%Begin%% Body
{
    %%Begin%% Programming
    \begin{LARGE}
        \color{em-light}\textbf{\\[-15pt]{\firamedium Development Experience}\\[-10pt]}
    \end{LARGE}

    \begin{tabularx}{\textwidth}{llX}
    \faDesktop\space\space{\bfseries {\firamedium Back End}}
        & {\color{darkgrey} \textbullet\space\space Python, Go, Node.js, PHP} & \\[5pt]
    \faDatabase\space\space{\bfseries {\firamedium Databases}}
        & {\color{darkgrey} \textbullet\space\space RDS, MongoDB, PostgreSQL, MySQL, CloudSQL, DynamoDB, Redis} & \\[5pt]
    \faCogs\space\space{\bfseries {\firamedium DevOps Tools}}
        & {\color{darkgrey} \textbullet\space\space Bash, Git, Prometheus, Thanos, Grafana, Loki, Tempo, Istio, GitLab CI, Github Actions, NGINX} & \\[2pt]
        & {\color{darkgrey} \textbullet\space\space Kubernetes, Terraform, ArgoCD, Docker, Cloudflare, Packer, Helm, kOps, Teleport, KinD} & \\[5pt]
    \faLinux\space\space{\bfseries {\firamedium Environments}}
        & {\color{darkgrey} \textbullet\space\space AWS: EC2, EKS, ECS, VPC, IAM, Route53, S3, Lambda, Cloudformation, etc.} & \\[2pt]
        & {\color{darkgrey} \textbullet\space\space Azure: AKS, ABS, DNS, Azure Cache for Redis, etc.} & \\[2pt]
        & {\color{darkgrey} \textbullet\space\space GCP: GKE, KMS, GCS, StackDriver, GCE, Pub-Sub, etc.} & \\[2pt]
    \faBook\space\space{\bfseries {\firamedium Fundamentals}}
        & {\color{darkgrey} \textbullet\space\space Cloud, Gitops, Microservices, CI/CD, Serverless Applications, Agile Development} & \\[10pt]
    \end{tabularx}
    %%End%% Programming
    %%Begin%% Experience
    {\color{lightgrey}{\centerline{\rule{17cm}{0.4pt}}}}
    \begin{LARGE}
        \color{em-light}\textbf{\\[-5pt]{\firamedium Work Experience}\\[-15pt]}
    \end{LARGE}

    \textbf{{\firamedium Site Reliability Engineer II at \textit{Mattermost}}}{\color{darkgrey}
    \hfill{\small{May 2022 to May 2023\\[-5pt]}} 
    \begin{tabularx}{\textwidth}{lp{16cm}X} 
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Maintained over 15,000 production Mattermost workspaces within Kubernetes. } & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Rearchitected Mattermost production services to be managed by ArgoCD.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Orchestrated design process to move Mattermost from Calico CNI to AWS VPC CNI.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Utilized Mattermost Operator to deploy workspaces in Kubernetes environments.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Productionalized Mattermost's Community installation to be more reliable, observable, and maintainable.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Led initiatives to convert internal tools to be cloud-native and host them within Kubernetes environments.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Participated in a weekly on-call rotation to respond to production alerts.} & \\ [-10pt]
    \end{tabularx}\\
    }

    \textbf{{\firamedium DevOps Engineer at \textit{Daylight}}}{\color{darkgrey}
    \hfill{\small{May 2020 to May 2022\\[-5pt]}} 
    \begin{tabularx}{\textwidth}{lp{16cm}X} 
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Planned migration of AWS services to Azure-hosted Kubernetes for all Daylight environments.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Designed architecture and deployment strategies for new Kubernetes environments.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Supported Shoppers Drug Mart Covid-19 testing and vaccination forms to handle heavy traffic.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Migrated existing cloudformation troposphere scripts to Terraform to manage all new environments.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Maintained existing, and created new AWS environments using EC2, ECS, VPC, Route53, and Cloudfront.} & \\ [-10pt]
    \end{tabularx}\\
    }

    \textbf{{\firamedium DevOps Engineer at \textit{Tulip Retail}}}{\color{darkgrey}
    \hfill{\small{January 2019 to April 2020\\[-5pt]}} 
    \begin{tabularx}{\textwidth}{lp{16cm}X} 
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Designed and built an SFTP Automation Framework leverging AWS services to remove manual configuration.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Built CI/CD frameworks for internal projects and all serverless applications through use of GitLab CI that automatically tests and deploys new changes.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Set up monitoring solution leveraging Prometheus, Thanos, Grafana, and Alertmanager.} & \\ [-5pt]
        & \color{em-light} \faGenderless\space\space \color{darkgrey}{Developed new metric exporters \& dashboards to alert on more metrics around Tulip's internal systems.} & \\ [-10pt]
    \end{tabularx}\\
    }

    \textbf{{\firamedium Conference Speaker at \textit{AWS Summit Toronto 2019}}}{\color{darkgrey}\hfill{\small{October 2019\\[5pt]}}
    \begin{tabularx}{\textwidth}{lp{16cm}X} 
        & As a conference speaker in the Start-up Booth at AWS Summit Toronto 2019 I presented my \textbf{SFTP Automation design} that solves the problem of manual easing work on existing SFTP Virtual Machine instances. This was achieved by leveraging many tools such as Transfer for AWS, Lambdas, DynamoDB, and SQS functionality. & \\[-10pt]
    \end{tabularx}\\
    }

    %%End%% Experience
    %%Begin%% Education
    {\color{lightgrey}{\centerline{\rule{17cm}{0.1pt}}}}
    \begin{LARGE}
        \color{em-light}\textbf{\\[-15pt]{\firamedium Education}\\[-15pt]}
    \end{LARGE}

    \textit{\textbf{{\firamedium University of Waterloo}}}{\color{darkgrey}{\hfill{\small{Graduated in 2018\\[0pt]}}
    Bachelor of Computer Science, Computer Science, Honours, Co-operative Program}\\[-20pt]}
    
    \textit{\textbf{{\firamedium Currently Reading}}}{\color{darkgrey}\\[0pt]
    {\textit{Kubernetes Best Practices}} by O'Reilly, {\textit{Cloud Native DevOps with Kubernetes}} by O'Reilly, and {\textit{Refactoring}} by M. Fowler \& K. Beck}
    %%End%% Education
}
%%End%% Body
\end{document}
